---
title: "Palmer Penguins"
author: "John Cruz"
date: "2023-02-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required Libraries

```{r library, warning=FALSE, message=FALSE}
library(tidyverse)
library(palmerpenguins)
```

Do penguins with longer flippers weigh more or less than penguins with shorter flippers? 

## Overview
``` {r dataframe}
df <- palmerpenguins::penguins

knitr::kable(head(df))
```

## Scatterplot of Body Mass vs. Flipper Length by Species

``` {r plot-flipper-vs-mass-by-species}
ggplot(df, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species, shape = species), na.rm = TRUE) +
  geom_smooth(na.rm = TRUE) +
  labs(title = "Body Mass vs. Flipper Length",
        subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
        x = "Flipper length (mm)",
        y = "Body mass (g)",
        color = "Species",
        shape = "Species")
```

## Scatterplot of Bill Depth vs. Bill Length

``` {r plot-bill_depth-bill_length}
ggplot(df, aes(x = bill_depth_mm, y = bill_length_mm)) +
  geom_point(na.rm = TRUE) +
  labs(title = "Bill Depth vs. Bill Length", 
       x = "Bill Depth (mm)", 
       y = "Bill Length (mm)",
       caption = "Data come from the palmerpenguins package.")
```

## Scatterplot of Flipper Length vs. Body Mass by Bill Depth

``` {r plot-flipper-mass-depth, warning=FALSE}
ggplot(df, aes(x = flipper_length_mm, y = body_mass_g, color = bill_depth_mm)) +
  geom_point() +
  geom_smooth() + 
  labs(title = "Flipper Length vs. Body Mass", 
       x = "Flipper Length (mm)", 
       y = "Body Mass (g)",
       color = 'Bill Depth (mm)')
```

## Count Plot of Penguin Species

``` {r plot-species-count}
ggplot(penguins, aes(x = fct_infreq(species))) +
  geom_bar() +
  labs(x = 'species')
```

## Distribution of Body Mass

``` {r hist-body_mass, warning=FALSE}
ggplot(penguins, aes(x = body_mass_g)) +
  geom_histogram(binwidth = 200)
```

## Looking at *geom_bar()* Color vs. Fill Attributes

``` {r color-vs-fill}
ggplot(penguins, aes(x = species)) +
  geom_bar(color = "red")

ggplot(penguins, aes(x = species)) +
  geom_bar(fill = "red")
```

## Distributions of Body Mass based on Species

``` {r boxplot, warning=FALSE}
ggplot(penguins, aes(x = species, y = body_mass_g)) +
  geom_boxplot()
```

## Population Proportion of Species to each Island

```{r stacked-plot-island-species, warning=FALSE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(position ='fill') +
  labs(y = '% of island population') +
  scale_y_continuous(labels = scales::percent)
```

## Weight and Flipper Length of Species to each Island

```{r facet_plot-species-island, warning=FALSE, echo=FALSE}
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species, shape = species)) +
  facet_wrap(~island) +
  theme(panel.spacing = unit(2, "lines"))

ggsave(filename = 'facet_plot_penguins.png')
```

## Weight and Flipper Length of Species to each Island

```{r test, warning=FALSE}
ggplot(
  data = penguins,
  mapping = aes(
    x = bill_length_mm, y = bill_depth_mm, 
    color = species, shape = species
  )
) +
  geom_point()
```











